SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-01 scipy-1.0/ckdtree.tex
Improvements to cKDTree paragraph 3
I have tried to shrink a bit paragraph 3.
I also removed the reference to `(sets of points organized into a binary space 
partitioning data structure\cite{Bentley:1975:MBS:361002.361007})` ... if we think we need a definition of what a kdtree is, maybe it is better to put it at the beginning of the section.

Also in 2015, SciPy added support for generating approximated sparse distance matrices 
between \texttt{KDTree} objects (sets of points organized into a binary space 
partitioning data structure\cite{Bentley:1975:MBS:361002.361007}). 
The user provides a maximum distance value
above which all distances between points in two provided \texttt{KDTree} objects
are set to 0. The distance metric used between k-d trees is not constrained
to the conventional L2 (Euclidean) norm---any Minkowski p-norm value
bounded by 1 and infinity is valid. By default, a dictionary of keys
based sparse matrix is the returned data structure. Previously-published
results had suggested that a hashing approach to sparse matrix assembly
is 7 times faster than constructing with compressed row format (CSR)\cite{10.1007/978-3-540-75755-9_107}.
The dictionary object maps row and column indices to elements of the sparse matrix, which is
efficient for matrix construction because all zero values are skipped in
the dictionary mapping. The C++ level sparse matrix construction releases the Python
global interpreter lock for increased performance. Once constructed, the
dictionary of keys sparse matrix has the amortized constant time complexity 
($O(1)$) for distance value retrieval that one would expect from a 
dictionary\cite{Cormen:2001:IA:580470}. For efficiently performing arithmetic
operations on the sparse matrix, SciPy allows the dictionary of keys
sparse matrix to be directly converted to the common CSR, CSC, and COO
data structures.

@@

>>>>

In 2015, SciPy added support for generating approximated sparse distance matrices 
between \texttt{KDTree} objects by zeroing all distances that exceed a user-provided value. 
The distance metric used between k-d trees is not constrained to the 
conventional L2 (Euclidean) norm---any Minkowski p-norm value bounded by 1 and 
infinity is valid. By default, the returned data structure is a dictionary of 
keys based sparse matrix, which is very efficient for matrix construction. 
Previously-published results had suggested that this hashing approach to sparse 
matrix assembly is 7 times faster than constructing with compressed row format (CSR)
\cite{10.1007/978-3-540-75755-9_107} and the C++ level sparse matrix construction 
releases the Python GIL for increased performance. Also, once the matrix is 
contructed, distance value retrieval has an amortized constant time complexity 
\cite{Cormen:2001:IA:580470}. For efficiently performing arithmetic operations 
on it, SciPy allows the sparse matrix to be directly converted to the common 
CSR, CSC and COO data structures.

@@

\fixme{Add a Figure to show the scaling, before and after.}
\fixme{perhaps give an example or some formula.}
(cite / mention faster implementions of paircounting algorithms / treecorr, corrfunc)

The main purpose of the paircounting algorithm in cKDTree is to provide a readily
available tool. The KDTree based algorithm is not necessarily the fastest algorithm
depending on the application. E.g. for low number densities a chaining mesh based algorithm
can be easily many times faster than a tree based algorithm.
